Investigating the Underprovision of Public Goods: Does Segregation Matter?

### 2020-04-29 Draft_1.Rmd
table lable changes

# fixed effects like a control variable

# lmer(dependent ~ predictors + (random predictors | group level))

# reml v. log likelihood: default in r appears to be log-likelihood. stata defaults to maximum likelihood

@@

```{r felm, eval = FALSE}

@@

```{r main_fp_tables, results = "asis", eval = FALSE}

@@

table2 <- stargazer(felm1, felm2, felm3, omit = c("year", "south", "midwest", "west"), 
                    header = FALSE,
                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}")

@@

```{r, eval = FALSE}

@@

```{r results = "asis", eval = FALSE}
table3a <- stargazer(felm2_1, felm2_2, felm2_3, 
          omit = c("year", "south", "midwest", "west"), 
          header = FALSE,
          title = "\\textbf{Effect of Segregation on Public Goods A}")

@@

```{r iv_regs, eval = FALSE}

@@

# Table 5

```{r results = "asis", echo = FALSE}

table5a <- stargazer(ivreg1, ivreg2, ivreg3, ivreg4,
          omit = c("y5", "y6", "y7", "y8", "y9", "northeast", "south", "midwest", "west"), 
          header = FALSE,
          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach A}")

table5b <- stargazer(ivreg5, ivreg6, ivreg7,
          omit = c("y5", "y6", "y7", "y8", "y9", "northeast","south", "midwest", "west"), 
          header = FALSE,
          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach B}")
```

@@

```{r include = FALSE, include = FALSE}

@@

```{r, echo = FALSE}
gt(a3_final) %>%
    tab_header(title = md("**TABLE A3 Summary Statistics: Census of Government Finance and Population**"),
             subtitle = "") %>%
    fmt_number(columns = vars(Mean, SD, Min, Max),
             decimals = 3) %>%
    cols_label(Obs = md("**Obs**"),
               Mean = md("**Mean**"),
               SD = md("**SD**"),
               Min = md("**Min**"),
               Max = md("**Max**")
                        ) 
```

>>>>

@@

```{r felm, include = FALSE}

@@

```{r main_fp_tables, results = "asis", echo = FALSE}

@@

table2 <- stargazer(felm1, felm2, felm3, omit = c("year", "south", "midwest", "west"), 
                    header = FALSE,
                    title = "\\textbf{Effect of Segregation on Overall per Capita City Expenditures}",
                covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Change Percent Black", "Change Percent Latino", "Change Percent Asian", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "White Ideology", "Constant"))

@@

```{r, include = FALSE}

@@

```{r results = "asis", echo = FALSE}
table3a <- stargazer(felm2_1, felm2_2, felm2_3, 
          omit = c("year", "south", "midwest", "west"), 
          header = FALSE,
          title = "\\textbf{Effect of Segregation on Public Goods A}",
          covariate.labels = c("White/Nonwhite H Index", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Population (logged)", "Constant"))

@@

```{r iv_regs, include = FALSE}

@@

```{r results = "asis", echo = FALSE, eval = FALSE}

table5a <- stargazer(ivreg1, ivreg2, ivreg3, ivreg4,
          omit = c("y5", "y6", "y7", "y8", "y9", "northeast", "south", "midwest", "west"), 
          header = FALSE,
          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach A}",
          covariate.labels = c("White/Nonwhite H Index", "Lagged Direct Gen. Exp.", "Lagged Highway Exp.", "Lagged Police Exp.", "Lagged Parks Exp.", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Constant"))

table5b <- stargazer(ivreg5, ivreg6, ivreg7,
          omit = c("y5", "y6", "y7", "y8", "y9", "northeast","south", "midwest", "west"), 
          header = FALSE,
          title = "\\textbf{Effect of Segregation on City Expenditures, IV Approach B}",
          covariate.labels = c("White/Nonwhite H Index", "Lagged Sewers Exp.", "Lagged Gen. Rev. Own Sources", "Lagged Police Exp.", "Lagged Welfare", "Diversity", "Percent Black", "Percent Asian", "Percent Latino", "Medain HH Income (1000s)", "Percent Government Worker", "Percent Renters", "Percent 65+", "Percent College Degree", "Constant"))
```

@@

```{r fp_summary_table, include = FALSE}

@@

```{r fp_summary_table_stargazer, echo = FALSE}
gt(a3_final) %>%
    tab_header(title = md("**TABLE A3 Summary Statistics: Census of Government Finance and Population**"),
             subtitle = "") %>%
    fmt_number(columns = vars(Mean, SD, Min, Max),
             decimals = 3) %>%
    cols_label(Obs = md("**Obs**"),
               Mean = md("**Mean**"),
               SD = md("**SD**"),
               Min = md("**Min**"),
               Max = md("**Max**")
                        ) 
```
